A pipeline to analyse time-course gene expression data

### 2020-08-19 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

The manuscript was last compile on 2020-08-11 06:50:22.

@@

\begin{tabular}{llrrrlr}
\toprule
GO ID & Description & Annotated & Significant & Expected & P-value & Adj. p-value\\
\midrule
GO:0019395 & fatty acid oxidation & 55 & 54 & 44.78 & 0.00016 & 0.164\\
GO:1905114 & cell surface receptor signaling pathway ... & 272 & 243 & 221.46 & 0.00021 & 0.179\\
GO:0003002 & regionalization & 174 & 158 & 141.67 & 0.00049 & 0.358\\
GO:0009755 & hormone-mediated signaling pathway & 82 & 77 & 66.76 & 0.00105 & 0.671\\
GO:0048562 & embryonic organ morphogenesis & 154 & 139 & 125.39 & 0.00175 & 0.994\\
\addlinespace
GO:0006805 & xenobiotic metabolic process & 50 & 48 & 40.71 & 0.00257 & 1.000\\
GO:0090596 & sensory organ morphogenesis & 138 & 124 & 112.36 & 0.00332 & 1.000\\
GO:0035108 & limb morphogenesis & 74 & 69 & 60.25 & 0.00337 & 1.000\\
GO:0030166 & proteoglycan biosynthetic process & 27 & 27 & 21.98 & 0.00385 & 1.000\\
GO:0003206 & cardiac chamber morphogenesis & 72 & 67 & 58.62 & 0.00448 & 1.000\\
\addlinespace
GO:0055114 & oxidation-reduction process & 536 & 472 & 436.41 & 0.00489 & 1.000\\
GO:0021954 & central nervous system neuron developmen... & 36 & 35 & 29.31 & 0.00557 & 1.000\\
GO:0006261 & DNA-dependent DNA replication & 70 & 64 & 56.99 & 0.00595 & 1.000\\
GO:0006633 & fatty acid biosynthetic process & 78 & 70 & 63.51 & 0.00686 & 1.000\\
GO:0006790 & sulfur compound metabolic process & 154 & 136 & 125.39 & 0.00710 & 1.000\\
\bottomrule
\end{tabular}

>>>>

The manuscript was last compile on 2020-08-19 18:14:47.

@@

\begin{tabular}{llrrrlr}
\toprule
GO ID & Description & Annotated & Significant & Expected & P-value & Adj. p-value\\
\midrule
GO:0003002 & regionalization & 175 & 159 & 142.49 & 0.00044 & 0.375\\
GO:0019395 & fatty acid oxidation & 58 & 56 & 47.22 & 0.00065 & 0.475\\
GO:0007224 & smoothened signaling pathway & 75 & 71 & 61.07 & 0.00083 & 0.530\\
GO:0048562 & embryonic organ morphogenesis & 154 & 139 & 125.39 & 0.00175 & 0.994\\
GO:0009755 & hormone-mediated signaling pathway & 76 & 71 & 61.88 & 0.00254 & 1.000\\
\addlinespace
GO:0006805 & xenobiotic metabolic process & 50 & 48 & 40.71 & 0.00257 & 1.000\\
GO:0006790 & sulfur compound metabolic process & 155 & 138 & 126.20 & 0.00317 & 1.000\\
GO:0060173 & limb development & 90 & 83 & 73.28 & 0.00325 & 1.000\\
GO:0018394 & peptidyl-lysine acetylation & 82 & 76 & 66.77 & 0.00336 & 1.000\\
GO:0030166 & proteoglycan biosynthetic process & 27 & 27 & 21.98 & 0.00386 & 1.000\\
\addlinespace
GO:0003206 & cardiac chamber morphogenesis & 72 & 67 & 58.62 & 0.00449 & 1.000\\
GO:0006633 & fatty acid biosynthetic process & 88 & 79 & 71.65 & 0.00580 & 1.000\\
GO:0006261 & DNA-dependent DNA replication & 71 & 65 & 57.81 & 0.00595 & 1.000\\
GO:0090596 & sensory organ morphogenesis & 139 & 124 & 113.18 & 0.00637 & 1.000\\
GO:0055114 & oxidation-reduction process & 541 & 475 & 440.49 & 0.00651 & 1.000\\
\bottomrule
\end{tabular}
